Measurement Bias from Address Aliasing

### 2014-05-17 paper.tex
Some work on improving allocator comparison

\begin{table}[t]
  \caption{Addresses returned by different heap allocators when allocating pairs of equally sized buffers}
  \label{tab:mallocompare}
  \centering
  \small
  \begin{tabular}{l r r}
    \toprule
                      & 5120 B          & $2^{20}$ B \\
    \midrule
    glibc             & 0x6028d0        & 0x2aaaaaaf3010 \\
    (ptmalloc)        & 0x603ce0        & 0x2aaaab098010 \\
    \midrule
    tcmalloc          & 0xe16000        & 0xe64000 \\
                      & 0xe18800        & 0xf64000 \\
    \midrule
    jemalloc          & 0x2aaaabc1f000  & 0x2aaaabc86000 \\
                      & 0x2aaaabc21000  & 0x2aaaabd86000 \\
    \midrule
    Hoard             & 0x2aaaaab40070  & 0x2aaaabf40070 \\
                      & 0x2aaaaab42070  & 0x2aaaac060070 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

% \begin{table}[t]
%   \caption{Addresses returned by different heap allocators when allocating pairs of equally sized buffers}
%   \label{tab:mallocompare}
%   \centering
%   \small
%   \begin{tabular}{l r r}
%     \toprule
%                       & 5120 B          & $2^{20}$ B \\
%     \midrule
%     glibc             & 0x6028d0        & 0x2aaaaaaf3010 \\
%     (ptmalloc)        & 0x603ce0        & 0x2aaaab098010 \\
%     \midrule
%     tcmalloc          & 0xe16000        & 0xe64000 \\
%                       & 0xe18800        & 0xf64000 \\
%     \midrule
%     jemalloc          & 0x2aaaabc1f000  & 0x2aaaabc86000 \\
%                       & 0x2aaaabc21000  & 0x2aaaabd86000 \\
%     \midrule
%     Hoard             & 0x2aaaaab40070  & 0x2aaaabf40070 \\
%                       & 0x2aaaaab42070  & 0x2aaaac060070 \\
%     \bottomrule
%   \end{tabular}
% \end{table}

\begin{table*}[t]
  \caption{Addresses returned by different heap allocators when allocating pairs of equally sized buffers.}
  \label{tab:mallocompare}

  %\renewcommand{\tabcolsep}{3pt} % Less padding between cells
  \pgfplotstabletypeset[
    font=\small,
    col sep=comma,
    string type,
    columns={Allocation, 64, 1024, 5120, 1048576},
    column type=r,
    columns/.style={
        width=1cm
    },
    columns/Allocation/.style={
      string type, 
      column type=l
    },
    every head row/.style={
      output empty row,
      before row={\toprule
         & 64 & 1024 & 5120 & 1048576 \\
        },
      after row=\midrule,
    },
    every last row/.style={after row=\bottomrule}
  ]{bin/malloc-comparison.csv}
\end{table*}
